---
title: "PeakSorter vignettes"
author: "Alan Tseng"
date: "September 12, 2017"
output: 
  html_vignette:
    toc: true

vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{PeakSorter vignettes}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
PeakSorter is a tool to process LC-MS peak lists so that
the most relevant peaks are at the top.

There are three sorting methods implemented in PeakSorter:

* Binned method (as described in unpublished manuscript) - `bin.prioritize`
* Intensity method (sort from highest to lowest intensity) - `intensity.prioritize`
* Random method (random order) - `random.prioritize`

Basic steps for using the PeakSorter R package:

1. Loading the package, your peak data, and set of true positive peaks (if desired)
2. Sorting using one or multiple sorting methods
3. Visualizing and validating results

# Load PeakSorter
```{r}
library(PeakSorter)
```

# Prepare input dataset
As an example, we'll sort the peak list from a metabolomics experiment
with Idh1 knock-in mouse plasma. This data is included in the package.

If you have your own peak list file, you can load that using the
`read.peak.file` function.

Please note:

* the columns must be named exactly as such
* retention time should be in minutes
* peak ID must be unique
* these criteria can be checked using the `check.peak.df` function

```{r}
# Inspect the Idh1 dataset
head(idh1)

# Validate the peak data frame
check.peak.df(idh1)
```

Here are the peaks whose m/z match known metabolites from [HMDB](http://www.hmdb.ca/) database (true positive peaks).
You can define your own custom set of true positive peaks.
This variable is only required for validating the peak sorting.

Note: all the peak IDs in the true positive set must appear in your peak data frame.
```{r}
head(idh1.true.pos)
```

# Sort the dataset using the binned method
```{r}
# Sort dataset using binned sort
sorted <- bin.prioritize(idh1)

# Look at the binned sorted dataset
head(sorted)

# Plot the top 100 peaks of the binned sorted dataset
peak.plot(list(Sorted=top.peaks(sorted)))

# Validate the sorted dataset
roc.auc(sorted, idh1.true.pos)
```

# Compare different sorting methods on the same dataset
```{r}
# Sort the IDH1 dataset using different methods
sorted.peaks <- list(
  Random=random.prioritize(idh1),
  Intensity=intensity.prioritize(idh1),
  Binned=bin.prioritize(idh1, 0.01) # Instead of 0.01 min., you can choose your own bin width
)
```

## Plot the sorted peaks
```{r}
# Also, can take the top 100 peaks from each sorted list
top100 <- lapply(sorted.peaks, top.peaks)

# Plot the top 100 peaks
peak.plot(top100)
```

## Validate the sorted peaks
```{r}
# Plot the receiver operating characteristic (ROC) curves
# of peaks sorted using different methods
roc.plot(sorted.peaks, idh1.true.pos)
```
