---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(PeakSorter)

# Locations of the files
output.dir <- "C:/Users/A.T/Documents/PleuralEffusion/PeakSorter"
peak.file <- file.path(output.dir, "Input.txt")
masstrix.file <- file.path(output.dir, "../MassTRIX/Output.txt")


set.seed(12345)

# Read the peaks from pleural effusion experiment
peak.df <- read.peak.file(peak.file)

# Sort the peaks using different methods
rand <- random.prioritize(peak.df)
intens <- intensity.prioritize(peak.df)
binned <- bin.prioritize(peak.df)

# Combine the sorted lists as one list
combined <- list(
  Random=rand,
  Intensity=intens,
  Binned=binned)
# Only take the top 100 peaks of each method
top100 <- lapply(combined, function(x) top.peaks(x, 100))

# Plot the intensity of each peak vs. retention time
peak.plot(top100)

# Plot dwell time boxplots
my.colours <- hsv(h=(1:3)/3, s=0.5, v=0.8)
dwell.time.boxplot(top100, col=my.colours)

# Load the mappable peaks from the MassTRIX data
annot <- read.csv(
  masstrix.file,
  header=TRUE, sep="\t")
mappable.peaks <- as.character(unique(annot$uniqueID))

# Create ROC curves for each method
roc.plot(combined, mappable.peaks)
```



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
